\begin{center}
\Large\textbf{ABSTRACT}
\end{center}
\vspace{1ex}

\begin{adjustwidth}{-0.2cm}{}
\begin{tabular}{lcp{0.6\linewidth}}
\textit{Name} &:& Robby Aldriyanto Raffly\\
\textit{Title} &:& \textit{Telecardiology App for Android Mobile Equipped with ECG Sensor} \\
\textit{Advisors} &:& 1. Arief Kurniawan, ST., MT. \\
& & 2. Dr. I Ketut Eddy Purnama, ST., MT. \\
\end{tabular}
\end{adjustwidth}
\vspace{1ex}

	\setlength{\parindent}{0cm}
	\textit{The heart is a very important organ for the body. Death from heart disease is one of the most common deaths in the world. Heart disease can be detected early by monitoring the heartbeat signal. In this final project, we propose a research title on the implementation of telecardiology systems. The implementation of the telecardiology system that we propose is to create an android application that can be used to retrieve ECG signal data from Arduino via the HC-05 bluetooth module. The ECG signal is obtained by Arduino using the AD8232 sensor. The application also has a feature to send an ECG signal to a cardiologist so that doctors can diagnose a patient's ECG signal without having to check the patient in person. The application also has a chat feature with doctors so that patients can consult remotely. The expected result of this research is that the application can retrieve data via bluetooth communication, send ECG signal data to doctors, and chat.} 
	\vspace{2ex}
	
	\textit{Keywords : Telecardiology, ECG, Signal Processing, Mobile Apps}
	\newpage
